Minimizing post shock forecasting error using disparate information

### 2020-05-28 manuscript/comp.tex
edit of manuscript and addition of simulation codes

% Created by tikzDevice version 0.12.3 on 2020-05-18 21:52:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.75,172.95) --
	( 68.63,152.47) --
	( 70.51,145.69) --
	( 72.39,140.03) --
	( 74.28,104.28) --
	( 76.16,151.54) --
	( 78.04,154.95) --
	( 79.92,133.81) --
	( 81.80,175.35) --
	( 83.69,166.88) --
	( 85.57,125.70) --
	( 87.45,170.76) --
	( 89.33,129.50) --
	( 91.22,171.48) --
	( 93.10,157.93) --
	( 94.98,132.20) --
	( 96.86,134.97) --
	( 98.74,121.20) --
	(100.63,132.31) --
	(102.51,167.74) --
	(104.39,139.43) --
	(106.27,161.95) --
	(108.15,118.76) --
	(110.04,173.04) --
	(111.92,101.84) --
	(113.80,132.79) --
	(115.68,156.33) --
	(117.57,121.16) --
	(119.45,173.74) --
	(121.33,100.01) --
	(123.21,122.32) --
	(125.09,136.35) --
	(126.98,148.45) --
	(128.86, 99.38) --
	(130.74,159.11) --
	(132.62,177.96) --
	(134.51,146.68) --
	(136.39, 99.65) --
	(138.27,141.14) --
	(140.15,113.97) --
	(142.03, 56.48) --
	(143.92,137.78) --
	(145.80,157.07) --
	(147.68,135.25) --
	(149.56,140.67) --
	(151.45,155.40) --
	(153.33,144.28) --
	(155.21,109.64) --
	(157.09,161.65) --
	(158.97,120.57) --
	(160.86,134.53) --
	(162.74,187.79) --
	(164.62,127.58) --
	(166.50,140.39) --
	(168.39,128.19) --
	(170.27,170.09) --
	(172.15,121.23) --
	(174.03,147.74) --
	(175.91,166.20) --
	(177.80,152.19) --
	(179.68, 95.16) --
	(181.56,137.35) --
	(183.44,180.08) --
	(185.32,152.17) --
	(187.21,170.34) --
	(189.09,168.84) --
	(190.97,130.81) --
	(192.85, 95.27) --
	(194.74,162.93) --
	(196.62,138.78) --
	(198.50,138.61) --
	(200.38,173.02) --
	(202.26,167.54) --
	(204.15,162.63) --
	(206.03,148.90) --
	(207.91,177.00) --
	(209.79,135.59) --
	(211.68,142.01) --
	(213.56,146.72) --
	(215.44,147.34) --
	(217.32,137.83) --
	(219.20,161.38) --
	(221.09,135.23) --
	(222.97,113.76) --
	(224.85,132.15) --
	(226.73,152.10) --
	(228.62,133.70) --
	(230.50,142.92) --
	(232.38,137.94) --
	(234.26, 80.23) --
	(236.14,128.05) --
	(238.03,140.12) --
	(239.91,113.33) --
	(241.79,135.32) --
	(243.67,145.57) --
	(245.56,148.21) --
	(247.44,181.13) --
	(249.32,123.87) --
	(251.20,167.03) --
	(253.08,176.92) --
	(254.97,146.67) --
	(256.85,137.49) --
	(258.73,148.71) --
	(260.61,158.20) --
	(262.49,144.01) --
	(264.38,140.56) --
	(266.26,134.50) --
	(268.14,164.72) --
	(270.02,113.97) --
	(271.91,173.50) --
	(273.79,131.97) --
	(275.67,135.32) --
	(277.55,143.59) --
	(279.43,134.00) --
	(281.32,182.28) --
	(283.20,134.50) --
	(285.08,136.30) --
	(286.96,121.98) --
	(288.85,170.76) --
	(290.73,168.83) --
	(292.61,130.32) --
	(294.49,130.95) --
	(296.37,167.83) --
	(298.26,106.18) --
	(300.14,158.89) --
	(302.02,221.32) --
	(303.90,262.43) --
	(305.79,181.52) --
	(307.67,221.00) --
	(309.55,219.36) --
	(311.43,223.97) --
	(313.31,225.88) --
	(315.20,172.43) --
	(317.08,211.80) --
	(318.96,229.45) --
	(320.84,222.24) --
	(322.73,252.46) --
	(324.61,190.77) --
	(326.49,224.11) --
	(328.37,194.35) --
	(330.25,184.33) --
	(332.14,175.51) --
	(334.02,208.94) --
	(335.90,208.16) --
	(337.78,210.48) --
	(339.67,204.77) --
	(341.55,200.42) --
	(343.43,207.20) --
	(345.31,194.28) --
	(347.19,175.97) --
	(349.08,221.82) --
	(350.96,230.52) --
	(352.84,206.54) --
	(354.72,213.96) --
	(356.60,241.92) --
	(358.49,206.43) --
	(360.37,254.17) --
	(362.25,205.63) --
	(364.13,199.30) --
	(366.02,207.87) --
	(367.90,210.32) --
	(369.78,198.03) --
	(371.66,248.03) --
	(373.54,206.39) --
	(375.43,246.52) --
	(377.31,210.82) --
	(379.19,232.38) --
	(381.07,213.29) --
	(382.96,237.01) --
	(384.84,208.79) --
	(386.72,192.52) --
	(388.60,236.32) --
	(390.48,175.56) --
	(392.37,250.12) --
	(394.25,185.69) --
	(396.13,231.06) --
	(398.01,191.78) --
	(399.90,226.76) --
	(401.78,199.54) --
	(403.66,165.06) --
	(405.54,255.85) --
	(407.42,210.34) --
	(409.31,199.91) --
	(411.19,229.86) --
	(413.07,203.76) --
	(414.95,231.64) --
	(416.84,230.77) --
	(418.72,190.26) --
	(420.60,203.84) --
	(422.48,209.53) --
	(424.36,220.43) --
	(426.25,173.24) --
	(428.13,209.84) --
	(430.01,159.64) --
	(431.89,251.30) --
	(433.77,197.02) --
	(435.66,216.20) --
	(437.54,224.42) --
	(439.42,193.29) --
	(441.30,213.98) --
	(443.19,172.72) --
	(445.07,245.00) --
	(446.95,192.05) --
	(448.83,235.97) --
	(450.71,204.00) --
	(452.60,164.26) --
	(454.48,238.03) --
	(456.36,185.07) --
	(458.24,227.07) --
	(460.13,222.82) --
	(462.01,212.73) --
	(463.89,268.60) --
	(465.77,192.34) --
	(467.65,239.77) --
	(469.54,202.33) --
	(471.42,231.75) --
	(473.30,220.58) --
	(475.18,187.28) --
	(477.07,206.99) --
	(478.95,199.08) --
	(480.83,226.56) --
	(482.71,221.75) --
	(484.59,227.59) --
	(486.48,203.00) --
	(488.36,227.21) --
	(490.24,209.56) --
	(492.12,221.87) --
	(494.01,245.38) --
	(495.89,236.19) --
	(497.77,241.22) --
	(499.65,231.39) --
	(501.53,253.76) --
	(503.42,191.19) --
	(505.30,203.77) --
	(507.18,247.46) --
	(509.06,219.46) --
	(510.94,214.21) --
	(512.83,191.34) --
	(514.71,248.79) --
	(516.59,197.34) --
	(518.47,220.12) --
	(520.36,259.69) --
	(522.24,240.39) --
	(524.12,221.17) --
	(526.00,214.51) --
	(527.88,259.99) --
	(529.77,220.91) --
	(531.65,215.72) --
	(533.53,233.07) --
	(535.41,219.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98, 48.00) -- (533.53, 48.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98, 48.00) -- ( 62.98, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.09, 48.00) -- (157.09, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.20, 48.00) -- (251.20, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.31, 48.00) -- (345.31, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.42, 48.00) -- (439.42, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (533.53, 48.00) -- (533.53, 42.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.98, 26.40) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (157.09, 26.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (251.20, 26.40) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (345.31, 26.40) {150};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (439.42, 26.40) {200};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (533.53, 26.40) {250};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.58) -- ( 48.00,270.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.58) -- ( 42.00, 55.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 98.61) -- ( 42.00, 98.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,141.64) -- ( 42.00,141.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,184.67) -- ( 42.00,184.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,227.69) -- ( 42.00,227.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,270.72) -- ( 42.00,270.72);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 55.58) {$-400$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 98.61) {$-200$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,141.64) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,184.67) {200};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,227.69) {400};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,270.72) {600};

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 66.75,142.83) --
	( 68.63,140.13) --
	( 70.51,141.93) --
	( 72.39,141.91) --
	( 74.28,142.43) --
	( 76.16,146.39) --
	( 78.04,141.61) --
	( 79.92,141.14) --
	( 81.80,143.78) --
	( 83.69,140.06) --
	( 85.57,141.28) --
	( 87.45,144.25) --
	( 89.33,140.02) --
	( 91.22,143.17) --
	( 93.10,140.45) --
	( 94.98,141.62) --
	( 96.86,143.92) --
	( 98.74,143.18) --
	(100.63,144.99) --
	(102.51,143.92) --
	(104.39,140.49) --
	(106.27,143.03) --
	(108.15,141.75) --
	(110.04,144.93) --
	(111.92,140.19) --
	(113.80,146.77) --
	(115.68,143.66) --
	(117.57,141.45) --
	(119.45,144.73) --
	(121.33,140.27) --
	(123.21,146.15) --
	(125.09,144.70) --
	(126.98,143.27) --
	(128.86,141.92) --
	(130.74,146.15) --
	(132.62,140.59) --
	(134.51,139.83) --
	(136.39,141.78) --
	(138.27,147.01) --
	(140.15,142.91) --
	(142.03,145.16) --
	(143.92,150.29) --
	(145.80,143.35) --
	(147.68,141.31) --
	(149.56,142.82) --
	(151.45,142.93) --
	(153.33,141.23) --
	(155.21,142.28) --
	(157.09,144.73) --
	(158.97,141.28) --
	(160.86,144.80) --
	(162.74,143.76) --
	(164.62,139.14) --
	(166.50,144.55) --
	(168.39,142.11) --
	(170.27,143.40) --
	(172.15,140.31) --
	(174.03,144.97) --
	(175.91,141.97) --
	(177.80,140.53) --
	(179.68,141.81) --
	(181.56,146.17) --
	(183.44,143.43) --
	(185.32,139.06) --
	(187.21,142.38) --
	(189.09,140.37) --
	(190.97,141.03) --
	(192.85,143.88) --
	(194.74,146.77) --
	(196.62,140.46) --
	(198.50,143.03) --
	(200.38,141.89) --
	(202.26,140.44) --
	(204.15,139.71) --
	(206.03,141.07) --
	(207.91,142.19) --
	(209.79,139.86) --
	(211.68,142.89) --
	(213.56,142.17) --
	(215.44,142.86) --
	(217.32,142.40) --
	(219.20,143.71) --
	(221.09,141.02) --
	(222.97,142.74) --
	(224.85,145.76) --
	(226.73,143.65) --
	(228.62,141.79) --
	(230.50,143.50) --
	(232.38,142.42) --
	(234.26,142.91) --
	(236.14,147.76) --
	(238.03,143.33) --
	(239.91,142.66) --
	(241.79,145.02) --
	(243.67,143.33) --
	(245.56,142.23) --
	(247.44,142.51) --
	(249.32,139.83) --
	(251.20,143.91) --
	(253.08,140.91) --
	(254.97,139.48) --
	(256.85,142.03) --
	(258.73,142.30) --
	(260.61,142.42) --
	(262.49,141.41) --
	(264.38,142.28) --
	(266.26,143.37) --
	(268.14,143.80) --
	(270.02,141.46) --
	(271.91,145.00) --
	(273.79,140.14) --
	(275.67,144.39) --
	(277.55,142.54) --
	(279.43,143.15) --
	(281.32,143.33) --
	(283.20,139.76) --
	(285.08,143.03) --
	(286.96,142.39) --
	(288.85,144.66) --
	(290.73,140.34) --
	(292.61,139.93) --
	(294.49,143.71) --
	(296.37,143.28) --
	(298.26,140.41) --
	(300.14,145.43) --
	(302.02,140.85) --
	(303.90,136.75) --
	(305.79,132.94) --
	(307.67,139.42) --
	(309.55,135.87) --
	(311.43,136.63) --
	(313.31,135.78) --
	(315.20,135.92) --
	(317.08,140.12) --
	(318.96,136.56) --
	(320.84,134.76) --
	(322.73,135.54) --
	(324.61,133.98) --
	(326.49,138.52) --
	(328.37,135.72) --
	(330.25,138.98) --
	(332.14,139.33) --
	(334.02,140.22) --
	(335.90,136.88) --
	(337.78,137.21) --
	(339.67,136.66) --
	(341.55,137.15) --
	(343.43,138.26) --
	(345.31,136.84) --
	(347.19,138.24) --
	(349.08,139.43) --
	(350.96,136.01) --
	(352.84,135.41) --
	(354.72,136.89) --
	(356.60,136.87) --
	(358.49,134.00) --
	(360.37,138.00) --
	(362.25,133.77) --
	(364.13,137.44) --
	(366.02,136.97) --
	(367.90,136.64) --
	(369.78,136.51) --
	(371.66,138.07) --
	(373.54,134.02) --
	(375.43,137.34) --
	(377.31,134.24) --
	(379.19,137.50) --
	(381.07,134.80) --
	(382.96,138.20) --
	(384.84,133.93) --
	(386.72,136.89) --
	(388.60,138.15) --
	(390.48,134.68) --
	(392.37,139.28) --
	(394.25,133.59) --
	(396.13,139.33) --
	(398.01,135.30) --
	(399.90,137.96) --
	(401.78,135.47) --
	(403.66,137.90) --
	(405.54,140.60) --
	(407.42,133.45) --
	(409.31,136.69) --
	(411.19,137.22) --
	(413.07,135.30) --
	(414.95,137.11) --
	(416.84,134.45) --
	(418.72,135.26) --
	(420.60,139.07) --
	(422.48,137.43) --
	(424.36,137.15) --
	(426.25,136.50) --
	(428.13,140.82) --
	(430.01,138.00) --
	(431.89,141.05) --
	(433.77,133.05) --
	(435.66,137.92) --
	(437.54,136.77) --
	(439.42,135.43) --
	(441.30,139.49) --
	(443.19,136.51) --
	(445.07,140.20) --
	(446.95,134.28) --
	(448.83,139.11) --
	(450.71,134.98) --
	(452.60,137.08) --
	(454.48,141.67) --
	(456.36,134.46) --
	(458.24,139.63) --
	(460.13,134.69) --
	(462.01,135.78) --
	(463.89,137.05) --
	(465.77,131.53) --
	(467.65,138.29) --
	(469.54,134.65) --
	(471.42,137.65) --
	(473.30,135.03) --
	(475.18,136.76) --
	(477.07,138.74) --
	(478.95,137.36) --
	(480.83,138.23) --
	(482.71,135.82) --
	(484.59,135.95) --
	(486.48,135.89) --
	(488.36,136.74) --
	(490.24,135.40) --
	(492.12,136.77) --
	(494.01,135.94) --
	(495.89,133.46) --
	(497.77,134.48) --
	(499.65,134.68) --
	(501.53,135.56) --
	(503.42,134.09) --
	(505.30,139.32) --
	(507.18,138.00) --
	(509.06,133.98) --
	(510.94,136.16) --
	(512.83,136.35) --
	(514.71,138.27) --
	(516.59,133.84) --
	(518.47,137.50) --
	(520.36,136.90) --
	(522.24,132.66) --
	(524.12,134.57) --
	(526.00,136.61) --
	(527.88,136.86) --
	(529.77,132.70) --
	(531.65,135.88) --
	(533.53,136.61) --
	(535.41,134.54);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 66.75,142.83) --
	( 68.63,140.13) --
	( 70.51,141.93) --
	( 72.39,141.91) --
	( 74.28,142.43) --
	( 76.16,146.39) --
	( 78.04,141.61) --
	( 79.92,141.14) --
	( 81.80,143.78) --
	( 83.69,140.06) --
	( 85.57,141.28) --
	( 87.45,144.25) --
	( 89.33,140.02) --
	( 91.22,143.17) --
	( 93.10,140.45) --
	( 94.98,141.62) --
	( 96.86,143.92) --
	( 98.74,143.18) --
	(100.63,144.99) --
	(102.51,143.92) --
	(104.39,140.49) --
	(106.27,143.03) --
	(108.15,141.75) --
	(110.04,144.93) --
	(111.92,140.19) --
	(113.80,146.77) --
	(115.68,143.66) --
	(117.57,141.45) --
	(119.45,144.73) --

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-27 15:30:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,150.94) --
	( 75.27,164.79) --
	( 78.11,157.49) --
	( 80.95,165.92) --
	( 83.79,166.40) --
	( 86.63,141.84) --
	( 89.47,150.09) --
	( 92.31,143.93) --
	( 95.15,141.05) --
	( 97.99,145.70) --
	(100.83,139.65) --
	(103.67,178.59) --
	(106.51,163.76) --
	(109.35,143.77) --
	(112.19,137.72) --
	(115.03,164.14) --
	(117.87,143.58) --
	(120.71,166.91) --
	(123.55,163.52) --
	(126.40,145.84) --
	(129.24,155.56) --
	(132.08,140.91) --
	(134.92,146.00) --
	(137.76,155.61) --
	(140.60,151.70) --
	(143.44,158.08) --
	(146.28,157.50) --
	(149.12,162.02) --
	(151.96,166.12) --
	(154.80,159.26) --
	(157.64,149.45) --
	(160.48,145.98) --
	(163.32,156.42) --
	(166.16,141.35) --
	(169.00,146.25) --
	(171.84,165.79) --
	(174.68,133.16) --
	(177.52,164.74) --
	(180.36,158.63) --
	(183.20,174.39) --
	(186.04,136.64) --
	(188.88,142.35) --
	(191.72,165.33) --
	(194.56,177.10) --
	(197.41,169.75) --
	(200.25,166.95) --
	(203.09,116.51) --
	(205.93,139.49) --
	(208.77,140.86) --
	(211.61,181.44) --
	(214.45,157.88) --
	(217.29,160.28) --
	(220.13,161.32) --
	(222.97,174.87) --
	(225.81,148.01) --
	(228.65,118.11) --
	(231.49,167.94) --
	(234.33,167.87) --
	(237.17,178.18) --
	(240.01,165.32) --
	(242.85,151.88) --
	(245.69,151.67) --
	(248.53,151.92) --
	(251.37,128.89) --
	(254.21,159.78) --
	(257.05,144.18) --
	(259.89,155.47) --
	(262.73,164.76) --
	(265.57,152.05) --
	(268.42,138.91) --
	(271.26,143.64) --
	(274.10,141.06) --
	(276.94,166.61) --
	(279.78,177.14) --
	(282.62,143.52) --
	(285.46,129.06) --
	(288.30,134.98) --
	(291.14,126.11) --
	(293.98,179.60) --
	(296.82,162.55) --
	(299.66,178.83) --
	(302.50,133.78) --
	(305.34,124.87) --
	(308.18,142.06) --
	(311.02,157.78) --
	(313.86,132.62) --
	(316.70,148.93) --
	(319.54,130.16) --
	(322.38,152.67) --
	(325.22,156.53) --
	(328.06,145.81) --
	(330.90,145.85) --
	(333.74,164.04) --
	(336.59,162.10) --
	(339.43,137.37) --
	(342.27,177.60) --
	(345.11,138.08) --
	(347.95,158.99) --
	(350.79,145.39) --
	(353.63,165.05) --
	(356.47,136.95) --
	(359.31,166.26) --
	(362.15,151.18) --
	(364.99,143.86) --
	(367.83,154.91) --
	(370.67,151.74) --
	(373.51,154.30) --
	(376.35,126.88) --
	(379.19,135.58) --
	(382.03,152.86) --
	(384.87,171.42) --
	(387.71,136.46) --
	(390.55,130.68) --
	(393.39,141.79) --
	(396.23,146.31) --
	(399.07,119.63) --
	(401.91,132.99) --
	(404.75,143.78) --
	(407.60,169.91) --
	(410.44,180.48) --
	(413.28,132.66) --
	(416.12,158.14) --
	(418.96,163.74) --
	(421.80,167.20) --
	(424.64,169.82) --
	(427.48,208.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 48.00) -- (492.81, 48.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 48.00) -- ( 66.75, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.77, 48.00) -- (208.77, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.79, 48.00) -- (350.79, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.81, 48.00) -- (492.81, 42.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (208.77, 26.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.79, 26.40) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 26.40) {150};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 48.00,265.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 42.00, 56.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 86.40) -- ( 42.00, 86.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,116.25) -- ( 42.00,116.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,146.10) -- ( 42.00,146.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,175.96) -- ( 42.00,175.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,205.81) -- ( 42.00,205.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,235.66) -- ( 42.00,235.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,265.51) -- ( 42.00,265.51);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 56.55) {-6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 86.40) {-4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,116.25) {-2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,146.10) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,175.96) {2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,205.81) {4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,235.66) {6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,265.51) {8};

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,150.71) --
	( 75.27,152.99) --
	( 78.11,153.34) --
	( 80.95,153.46) --
	( 83.79,154.87) --
	( 86.63,154.01) --
	( 89.47,150.03) --
	( 92.31,152.38) --
	( 95.15,151.57) --
	( 97.99,152.37) --
	(100.83,152.36) --
	(103.67,150.86) --
	(106.51,156.31) --
	(109.35,153.24) --
	(112.19,151.49) --
	(115.03,151.36) --
	(117.87,153.65) --
	(120.71,151.38) --
	(123.55,152.92) --
	(126.40,153.78) --
	(129.24,151.96) --
	(132.08,152.95) --
	(134.92,151.02) --
	(137.76,151.57) --
	(140.60,152.69) --
	(143.44,152.68) --
	(146.28,153.09) --
	(149.12,152.91) --
	(151.96,153.40) --
	(154.80,153.72) --
	(157.64,154.05) --
	(160.48,150.47) --
	(163.32,151.15) --
	(166.16,154.68) --
	(169.00,150.91) --
	(171.84,152.67) --
	(174.68,154.71) --
	(177.52,150.54) --
	(180.36,152.87) --
	(183.20,154.34) --
	(186.04,155.31) --
	(188.88,151.72) --
	(191.72,150.98) --
	(194.56,153.67) --
	(197.41,154.62) --
	(200.25,153.87) --
	(203.09,154.64) --
	(205.93,147.78) --
	(208.77,151.29) --
	(211.61,149.62) --
	(214.45,154.76) --
	(217.29,154.96) --
	(220.13,152.57) --
	(222.97,154.38) --
	(225.81,154.97) --
	(228.65,151.07) --
	(231.49,147.57) --
	(234.33,153.88) --
	(237.17,154.51) --
	(240.01,156.10) --
	(242.85,153.60) --
	(245.69,152.48) --
	(248.53,152.70) --
	(251.37,150.55) --
	(254.21,150.42) --
	(257.05,153.27) --
	(259.89,150.70) --
	(262.73,154.55) --
	(265.57,152.18) --
	(268.42,153.01) --
	(271.26,149.72) --
	(274.10,153.84) --
	(276.94,151.75) --
	(279.78,152.74) --
	(282.62,153.59) --
	(285.46,151.51) --
	(288.30,150.68) --
	(291.14,149.01) --
	(293.98,151.89) --
	(296.82,154.30) --
	(299.66,153.42) --
	(302.50,155.56) --
	(305.34,151.16) --
	(308.18,147.57) --
	(311.02,152.92) --
	(313.86,151.71) --
	(316.70,150.02) --
	(319.54,152.22) --
	(322.38,150.09) --
	(325.22,153.11) --
	(328.06,152.16) --
	(330.90,151.37) --
	(333.74,150.41) --
	(336.59,154.30) --
	(339.43,152.44) --
	(342.27,151.58) --
	(345.11,154.49) --
	(347.95,149.53) --
	(350.79,154.05) --
	(353.63,151.10) --
	(356.47,153.07) --
	(359.31,150.01) --
	(362.15,155.43) --
	(364.99,152.12) --
	(367.83,150.94) --
	(370.67,152.10) --
	(373.51,151.70) --
	(376.35,154.23) --
	(379.19,148.51) --
	(382.03,151.49) --
	(384.87,151.86) --
	(387.71,153.13) --
	(390.55,150.34) --
	(393.39,150.97) --
	(396.23,151.09) --
	(399.07,151.14) --
	(401.91,148.35) --
	(404.75,150.18) --
	(407.60,150.74) --
	(410.44,154.68) --
	(413.28,156.36) --
	(416.12,149.02) --
	(418.96,152.85) --
	(421.80,153.32) --
	(424.64,153.53) --
	(427.48,154.47);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,150.71) --
	( 75.27,152.99) --
	( 78.11,153.34) --
	( 80.95,153.46) --
	( 83.79,154.87) --
	( 86.63,154.01) --
	( 89.47,150.03) --
	( 92.31,152.38) --
	( 95.15,151.57) --
	( 97.99,152.37) --
	(100.83,152.36) --
	(103.67,150.86) --
	(106.51,156.31) --
	(109.35,153.24) --
	(112.19,151.49) --
	(115.03,151.36) --
	(117.87,153.65) --
	(120.71,151.38) --
	(123.55,152.92) --
	(126.40,153.78) --
	(129.24,151.96) --
	(132.08,152.95) --
	(134.92,151.02) --
	(137.76,151.57) --
	(140.60,152.69) --
	(143.44,152.68) --
	(146.28,153.09) --
	(149.12,152.91) --
	(151.96,153.40) --
	(154.80,153.72) --
	(157.64,154.05) --
	(160.48,150.47) --
	(163.32,151.15) --
	(166.16,154.68) --
	(169.00,150.91) --
	(171.84,152.67) --
	(174.68,154.71) --
	(177.52,150.54) --
	(180.36,152.87) --
	(183.20,154.34) --
	(186.04,155.31) --
	(188.88,151.72) --
	(191.72,150.98) --
	(194.56,153.67) --
	(197.41,154.62) --
	(200.25,153.87) --
	(203.09,154.64) --
	(205.93,147.78) --
	(208.77,151.29) --
	(211.61,149.62) --
	(214.45,154.76) --
	(217.29,154.96) --
	(220.13,152.57) --
	(222.97,154.38) --
	(225.81,154.97) --
	(228.65,151.07) --
	(231.49,147.57) --
	(234.33,153.88) --
	(237.17,154.51) --
	(240.01,156.10) --
	(242.85,153.60) --
	(245.69,152.48) --
	(248.53,152.70) --
	(251.37,150.55) --
	(254.21,150.42) --
	(257.05,153.27) --
	(259.89,150.70) --
	(262.73,154.55) --
	(265.57,152.18) --
	(268.42,153.01) --
	(271.26,149.72) --
	(274.10,153.84) --
	(276.94,151.75) --
	(279.78,152.74) --
	(282.62,153.59) --
	(285.46,151.51) --
	(288.30,150.68) --
	(291.14,149.01) --
	(293.98,151.89) --
	(296.82,154.30) --
	(299.66,153.42) --
	(302.50,155.56) --
	(305.34,151.16) --
	(308.18,147.57) --
	(311.02,152.92) --
	(313.86,151.71) --
	(316.70,150.02) --
	(319.54,152.22) --
	(322.38,150.09) --
	(325.22,153.11) --
	(328.06,152.16) --
	(330.90,151.37) --
	(333.74,150.41) --
	(336.59,154.30) --
	(339.43,152.44) --
	(342.27,151.58) --
	(345.11,154.49) --
	(347.95,149.53) --
	(350.79,154.05) --
	(353.63,151.10) --
	(356.47,153.07) --
	(359.31,150.01) --
	(362.15,155.43) --
	(364.99,152.12) --
	(367.83,150.94) --
	(370.67,152.10) --
	(373.51,151.70) --
	(376.35,154.23) --
	(379.19,148.51) --
	(382.03,151.49) --
	(384.87,151.86) --
	(387.71,153.13) --
	(390.55,150.34) --
	(393.39,150.97) --
	(396.23,151.09) --
	(399.07,151.14) --
	(401.91,148.35) --
	(404.75,150.18) --
	(407.60,150.74) --
	(410.44,154.68) --
	(413.28,156.36) --
	(416.12,149.02) --
	(418.96,152.85) --
	(421.80,153.32) --
	(424.64,153.53) --
	(427.48,232.35);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (424.64, 56.48) -- (424.64,268.60);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,225.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,235.83) circle (  2.25);
